Parallel Deduplication with Batch Scheduling for Collocated Virtual Machine Backup in the Cloud

### 2014-01-17 batchdedup/scheduling.tex
update size distribution chart with density function to compute bins

\begin{figure}[ht]
  \centering
  \begin{tikzpicture}
      \begin{axis}[
              ybar interval,
              xlabel=Avg VM Size in Group (GB),
              ylabel=Number of Groups,
              xticklabel={\pgfmathparse{(\tick*1)}\num[round-mode=places, round-precision=0]{\pgfmathresult}}
      ]
          \addplot+[hist={bins=10}] table[y=AY41G] {figures/cluster_distributions.txt};
      \end{axis}
  \end{tikzpicture}
  \caption{Histogram of average data sizes for a real cluster. TODO:adjust this using the new spreadsheets}
  \label{fig:hist-1}
\end{figure}

>>>>

%\begin{figure}[ht]
%  \centering
%  \begin{tikzpicture}
%      \begin{axis}[
%              ybar interval,
%              xlabel=Avg VM Size in Group (GB),
%              ylabel=Number of Groups,
%              xticklabel={\pgfmathparse{(\tick*1)}\num[round-mode=places, round-precision=0]{\pgfmathresult}}
%      ]
%          \addplot+[hist={bins=10}] table[y=AY41G] {figures/cluster_distributions.txt};
%      \end{axis}
%  \end{tikzpicture}
%  \caption{Histogram of average data sizes for a real cluster. TODO:adjust this using the new spreadsheets}
%  \label{fig:hist-1}
%\end{figure}

\begin{figure}[ht]
  \centering
  \begin{tikzpicture}
      \begin{axis}[
              ybar interval,
              xlabel=VM Size (GB),
              ylabel=Probability Distribution,
              xtick={50,100,200,300,400,500,600,700,800,900,1000},
      ]
          \addplot+[fill=blue] table[x=MinSize,y=Prob] {figures/AY41A_PD.txt};
      \end{axis}
  \end{tikzpicture}
  \caption{Histogram of average data sizes for a real cluster. TODO:adjust this using the new spreadsheets}
  \label{fig:hist-1}
\end{figure}

%xticklabel={\pgfmathparse{(\tick*1)}\num[round-mode=places, round-precision=0]{\pgfmathresult}}
